---
title: "Tables & Equations"
output:
  bookdown::pdf_document2:
    toc: false
linkcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Library

```{r lib}
library(tidyverse)
library(stargazer) # for reg table
library(MASS) # for data
library(gapminder)# for data
```



# Tables

## Regression table with `stargazer()`

We will use [25.8 An Example](https://af-ucp.courses/brm/ldv.html#anexample001)

```{r models}
# ols
m0 <- lm(low ~ smoke + race + ht + ui + ftv + age + lwt,
         data = birthwt)
# logit
m1 <- glm(low ~ smoke + race + ht + ui + ftv + age + lwt,
          data = birthwt,
          family = binomial(link = "logit"))
# probit
m2 <- glm(low ~ smoke + race + ht + ui + ftv + age + lwt,
          data = birthwt,
          family = binomial(link = "probit"))
```


```{r regtable, results='asis'}
stargazer::stargazer(m0, m1, m2, 
                     type = "latex", # "html" for html
                     title = "Results",
                     header = FALSE,
                     label = "tab:regression1")
```


## Stat table with `kable()`

We will use the `gapminder::gapminder` data.

```{r prepare-stat}
df <- gapminder::gapminder %>%
  filter(year >= 2000) %>% 
  group_by(year, continent) %>% 
  summarise(mean_life_exp = mean(lifeExp)) %>% 
  pivot_wider(
    names_from = year,
    values_from = mean_life_exp
  )
```


```{r stat-table}
knitr::kable(df,
             booktabs = TRUE,
             caption = 'Simple Stat Table')
```

# Cross Ref

Table \@ref(tab:regression1) presents blah blah; Table \@ref(tab:stat-table) presents blah blah.
 

# Dynamic Number

We will work with the logit model `m1`. Suppose you want to extract the coefficient of age.

Note that there are many ways to achieve it. I just present some examples.

## Using `broom`

```{r broom-m1}
broom::tidy(m1)
```



```{r broom-coeff-age}
broom::tidy(m1)[7,2]# returns a tibble
broom::tidy(m1)[7,2] %>% pull() # returns a vector

```


- The coefficient of age is `r broom::tidy(m1)[7,2]`

- The coefficient of age is `r broom::tidy(m1)[7,2] %>% pull()`

We can use `round()` to round the number. For example `round()` with `digits = 3` gives the following

- The coefficient of age is `r round(broom::tidy(m1)[7,2], digits  = 3)`

## Using base R

```{r base-m1}
summary(m1)
```
```{r}
summary(m1)$coefficients[7, 1] # returns a vector
```
- The coefficient of age is `r summary(m1)$coefficients[7, 1]`

- The coefficient of age is `r m1$coefficients[7]`

# Equations

## inline equation: `$ equation $`

In physics, the mass-energy equivalence is stated 
by the equation $E=mc^2$, discovered in 1905 by Albert Einstein.

## display equation : `$$ equation $$`

In physics, the mass-energy equivalence is stated 
by the equation $$E=mc^2,$$ discovered in 1905 by Albert Einstein.

## Cross Ref

\begin{equation} 
 y = X\beta + u
 (\#eq:ols)
\end{equation} 


\begin{equation} 
 \left(x+a\right)^n=\sum_{k=0}^{n}{\binom{n}{k}x^ka^{n-k}}
 (\#eq:binomial)
\end{equation} 

See equations \@ref(eq:ols) and \@ref(eq:binomial). 